Supplementary Information 1

### 2025-04-03 index.Rmd
adding text

```{r fig.width=9, fig.height=4}
dat1_std <- dat1$CPUE %>%
  mutate(
    # Standardize 'obs' between 0 and 1
    index_std = (obs - min(obs)) / (max(obs) - min(obs)),

    # Recode 'index' values
    index = recode(index,
                   `1` = "FISHERYBS",
                   `2` = "FISHERYEI",
                   `3` = "FISHERYGS",
                   `4` = "FISHERYJOIN",
                   `5` = "FISHERYSSIW",
                   `6` = "SURVEYBS",
                   `7` = "SURVEYEI",
                   `8` = "SURVEYGS",
                   `9` = "SURVEYJOIN",
                   `10` = "SURVEYSSIW",
                   `11` = "PREDATOR"),

    # Convert 'index' to a factor with specific levels
    index = factor(index, levels = c("FISHERYBS", 
                                     "FISHERYEI", 
                                     "FISHERYGS",
                                     "FISHERYJOIN", 
                                     "FISHERYSSIW", 
                                     "SURVEYBS", 
                                     "SURVEYEI", 
                                     "SURVEYGS", 
                                     "SURVEYJOIN", 
                                     "SURVEYSSIW", 
                                     "PREDATOR")),

    # Assign categories based on 'index'
    category = case_when(
      index %in% c("FISHERYBS", "FISHERYEI", "FISHERYGS", "FISHERYJOIN", "FISHERYSSIW") ~ "Fishery",
      index %in% c("SURVEYBS", "SURVEYEI", "SURVEYGS", "SURVEYJOIN", "SURVEYSSIW") ~ "Survey",
      index == "PREDATOR" ~ "Predator",
      TRUE ~ NA_character_  # In case there are any unexpected values
    )
  )

# Gráfico con 3 filas, dejando 'PREDATOR' en la última fila
ggplot(dat1_std, aes(x = year, y = index_std, group = index, color = category)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~index, scales = "free_y", ncol = 5) +  # Ajusta ncol para obtener 3 filas
  scale_color_manual(values = c("Fishery" = '#1b9e77', 
                                "Survey" = '#d95f02',
                                "Predator" = '#7570b3')) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "", x = "", y = "Standard index", color = "Category")

@@

ggplot(dat_expanded, aes(x = Talla, y = as.factor(Yr), fill = FltSvy)) +
  geom_density_ridges_gradient(scale = 1.8,
                               rel_min_height = 0.001,
                               col = "black",
                               alpha=0.4) +
  facet_wrap(~FltSvy, ncol = 10) +
  geom_vline(data = mean_talla, aes(xintercept = mean_Talla), 
             color = "red", 
             size = 0.7,
             alpha = 0.5) +
  scale_fill_manual(values = c("FISHERYBS" = '#1b9e77',  
                               "FISHERYEI" = '#1b9e77',  
                               "FISHERYGS" = '#1b9e77',
                               "FISHERYJOIN" = '#1b9e77',  
                               "FISHERYSSIW" = '#1b9e77',  
                               "SURVEYBS" = '#d95f02',  
                               "SURVEYEI" = '#d95f02',  
                               "SURVEYGS" = '#d95f02',  
                               "SURVEYJOIN" = '#d95f02',  
                               "SURVEYSSIW" = '#d95f02',  
                               "PREDATOR" = '#7570b3')) +  
  labs(title = "",
       x = "cm",
       y = "",
       fill = "Category") +
  theme_few()+
  theme(legend.position = "none")

@@

Data used en both (spatial and No spatial models) `s1.1`

```{r }
SSplotData(base.model1.1, 
           subplots = 1,
           pheight = 15)
```

and `s1.4`

```{r }
SSplotData(base.model1.4, 
           subplots = 1,
           pheight = 15)
```

@@

par(mfrow=c(1,3), mar=c(5,4,1,1)) 
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.2,
                 subplot = 1)
SSplotTimeseries(base.model1.2,
                 subplot = 9)
SSplotTimeseries(base.model1.2,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

@@

```{r}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.4,
                 subplot = 1)
SSplotTimeseries(base.model1.4,
                 subplot = 9)
SSplotTimeseries(base.model1.4,
                 subplot = 7)
```
Selectivity

```{r}
par(mfrow=c(2,2), mar=c(5,4,1,1))
SSplotSelex(base.model1.1,
            subplots = 1)
mtext("s1.1", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.2,
            subplots = 1)
mtext("s1.2", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.3,
            subplots = 1)
mtext("s1.3", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.4,
            subplots = 1)
mtext("s1.4", side=3, line=0.5, cex=1.2)
```

@@

# Combine the results from all models into one table
tablebias_combined <- bind_rows(
  data.frame(Model = "s1.1", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.1", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.4", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.4",
             Quant = "F", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "F", verbose = F))
)
```

@@

```{r eval=FALSE}
#### R0_profile_plot_Survey_like ----
png(file.path(plotdir,"R0_profile_plot_Survey_like.png"),
    width=7,
    height=4.5,
    res=300,
    units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, 
          profile.string = "R0", 
          component = "Surv_like",
          main = "Changes in Index likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95, legendloc="topleft")
Baseval <- round(Base$parameters$Value[grep("SR_LN",
                                            Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
```
## Outputs

@@

@@

@@

#create summary of model runs from list above
summaryoutputall <- SSsummarize(biglist)
```

```{r}
comtable <- SStableComparisons(summaryoutputall,
                   likenames = c("TOTAL", 
                                 "Survey", 
                                 "Length_comp",
                                 "Age_comp", 
                                 "priors",
                                 "Size_at_age"), 
                   names = c("Recr_Virgin",
                             "R0", 
                             "steep",
                             "NatM",
                             "L_at_Amax", 
                             "VonBert_K", 
                             "SSB_Virg", 
                             "Bratio_2020",
                             "SPRratio_2020"),
                   digits = NULL,
                   modelnames = c("s1.1", "s1.2",
                                  "s1.3",
                                  "s1.4"),
                   csv = F,
                   csvdir =~"/DOCAS/SA_Krill",
                   csvfile = "parameter_comparison_table.csv",
                 verbose = TRUE,
                   mcmc = FALSE)

kbl(comtable, booktabs = T,format = "latex",
    caption = "Comparision s1.1, s1.2, s1.3, s1.4")  %>% 
    kable_styling(latex_options = "scale_down")

@@

### Comparsion in sd long term time series

```{r fig.height=6, fig.width=8}

sblt1 <-  base.model1.1$timeseries$Bio_all
sblt2 <-  base.model1.2$timeseries$Bio_all
sblt3 <-  base.model1.3$timeseries$Bio_all
sblt4 <-  base.model1.4$timeseries$Bio_all

errt <- as.data.frame(cbind(sblt1,
              sblt2,
              sblt3,
              sblt4))
err_long <- errt %>%
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "value")  
titles <- c("Ref Model: No Env-Predator",
                 "S1.1 w/ Predator data",
                 "S1.1 w/ Env data",
                 "S1.1 w/ Env and Predator data")
ggplot(err_long, aes(x = variable, y = value)) +
  geom_boxplot(width=0.5) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(title = "Long Term Predictions",
       x = "",
       y = "Spawning Biomass (t)") +
  theme_few() +
  scale_x_discrete(labels= titles)+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1))
```

@@

df1 <- base.model1.1$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.1$likelihoods_used), Modelo = "s1.1")

df2 <- base.model1.2$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.2$likelihoods_used), Modelo = "s1.2")

df3 <- base.model1.3$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.3$likelihoods_used), Modelo = "s1.3")

df4 <- base.model1.4$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.4$likelihoods_used), Modelo = "s1.4")

df <- bind_rows(df1, 
                df2,
                df3,
                df4)

ggplot(df, aes(x = Componente, y = values, fill = Modelo)) +
  geom_col(position = position_dodge(), width = 0.7) +  
  theme_few() +
  coord_flip() +  
  scale_fill_manual(name= "Scenario",
                    values = c("s1.1" = '#ca0020',
                               "s1.2" = '#f4a582', 
                               "s1.3" = '#bababa',
                               "s1.4" = '#404040')) + 
  labs(x = "",
       y = "Log-Normal Likelihood", 
       title = "") 
```

>>>>

```{r fig.width=9, fig.height=4}
dat1_std <- dat1$CPUE %>%
  mutate(
    index_std = (obs - min(obs)) / (max(obs) - min(obs)),
    index = recode(index,
                   `1` = "FISHERYBS",
                   `2` = "FISHERYEI",
                   `3` = "FISHERYGS",
                   `4` = "FISHERYJOIN",
                   `5` = "FISHERYSSIW",
                   `6` = "SURVEYBS",
                   `7` = "SURVEYEI",
                   `8` = "SURVEYGS",
                   `9` = "SURVEYJOIN",
                   `10` = "SURVEYSSIW",
                   `11` = "PREDATOR"),
    index = factor(index, levels = c("FISHERYBS", 
                                     "FISHERYEI", 
                                     "FISHERYGS",
                                     "FISHERYJOIN", 
                                     "FISHERYSSIW", 
                                     "SURVEYBS", 
                                     "SURVEYEI", 
                                     "SURVEYGS", 
                                     "SURVEYJOIN", 
                                     "SURVEYSSIW", 
                                     "PREDATOR")),
    category = case_when(
      index %in% c("FISHERYBS", "FISHERYEI", "FISHERYGS", "FISHERYJOIN", "FISHERYSSIW") ~ "Fishery",
      index %in% c("SURVEYBS", "SURVEYEI", "SURVEYGS", "SURVEYJOIN", "SURVEYSSIW") ~ "Survey",
      index == "PREDATOR" ~ "Predator",
      TRUE ~ NA_character_  
    )
  )

p1 <- ggplot(dat1_std, aes(x = year, y = index_std, group = index, color = category)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~index, scales = "free_y", ncol = 5) +  # Ajusta ncol para obtener 3 filas
  scale_color_manual(values = c("Fishery" = '#1b9e77', 
                                "Survey" = '#d95f02',
                                "Predator" = '#7570b3')) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "", x = "", y = "Standard index", color = "Category")
p1
```

@@

p2 <- ggplot(dat_expanded, aes(x = Talla, y = as.factor(Yr), fill = FltSvy)) +
  geom_density_ridges_gradient(scale = 1.8,
                               rel_min_height = 0.001,
                               col = "black",
                               alpha=0.4) +
  facet_wrap(~FltSvy, ncol = 10) +
  geom_vline(data = mean_talla, aes(xintercept = mean_Talla), 
             color = "red", 
             size = 0.7,
             alpha = 0.5) +
  scale_fill_manual(values = c("FISHERYBS" = '#1b9e77',  
                               "FISHERYEI" = '#1b9e77',  
                               "FISHERYGS" = '#1b9e77',
                               "FISHERYJOIN" = '#1b9e77',  
                               "FISHERYSSIW" = '#1b9e77',  
                               "SURVEYBS" = '#d95f02',  
                               "SURVEYEI" = '#d95f02',  
                               "SURVEYGS" = '#d95f02',  
                               "SURVEYJOIN" = '#d95f02',  
                               "SURVEYSSIW" = '#d95f02',  
                               "PREDATOR" = '#7570b3')) +  
  labs(title = "",
       x = "cm",
       y = "",
       fill = "Category") +
  theme_bw()+
  theme(legend.position = "none")
p2
```

@@

Data used en both (spatial and No spatial models) `s1.1` and `s1.4` to compare

```{r }
par(mfrow=c(1,2), mar=c(5,4,2,1))
SSplotData(base.model1.1, 
           subplots = 1,
           pheight = 15)

SSplotData(base.model1.4, 
           subplots = 1,
           pheight = 15)
```

@@

```{r fig.height=3, fig.width=7}
par(mfrow=c(1,3), mar=c(5,4,1,1)) 
SSplotTimeseries(base.model1.1,
                 subplot = 1)
SSplotTimeseries(base.model1.1,
                 subplot = 9)
SSplotTimeseries(base.model1.1,
                 subplot = 7)
```

@@

```{r fig.height=3, fig.width=7}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.2,
                 subplot = 1)
SSplotTimeseries(base.model1.2,
                 subplot = 9)
SSplotTimeseries(base.model1.2,
                 subplot = 7)
```

@@

```{r fig.height=3, fig.width=7}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

@@

```{r fig.height=3, fig.width=7}
par(mfrow=c(1,3), mar=c(5,4,1,1))
SSplotTimeseries(base.model1.4,
                 subplot = 1)
SSplotTimeseries(base.model1.4,
                 subplot = 9)
SSplotTimeseries(base.model1.4,
                 subplot = 7)
```
Selectivity

```{r}
par(mfrow=c(2,2), mar=c(5,4,1,1))
SSplotSelex(base.model1.1,
            subplots = 1)
mtext("s1.1", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.2,
            subplots = 1)
mtext("s1.2", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.3,
            subplots = 1)
mtext("s1.3", side=3, line=0.5, cex=1.2)
SSplotSelex(base.model1.4,
            subplots = 1)
mtext("s1.4", side=3, line=0.5, cex=1.2)
```
```{r}
SSplotBiology(base.model1.1,
            subplots = 24)
```

Natural Mortality

```{r}
par(mfrow=c(2,2), mar=c(5,4,1,1))
SSplotBiology(base.model1.1,
            subplots = 21)
mtext("s1.1", side=3, line=0.5, cex=1.2)
SSplotBiology(base.model1.2,
            subplots = 21)
mtext("s1.2", side=3, line=0.5, cex=1.2)
SSplotBiology(base.model1.3,
            subplots = 21)
mtext("s1.3", side=3, line=0.5, cex=1.2)
SSplotBiology(base.model1.4,
            subplots = 21)
mtext("s1.4", side=3, line=0.5, cex=1.2)
```

@@

# Combine the results from all models into one table
tablebias_combined <- bind_rows(
  data.frame(Model = "s1.1", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.1", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.1, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.2", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.2, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.3", 
             Quant = "F", 
             Rho = SShcbias(retroSummary1.3, 
                            quant = "F", verbose = F)),
  data.frame(Model = "s1.4", 
             Quant = "SSB", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "SSB", verbose = F)),
  data.frame(Model = "s1.4",
             Quant = "F", 
             Rho = SShcbias(retroSummary1.4, 
                            quant = "F", verbose = F))
)
```
Viz

```{r}
tablebias_combined <- tablebias_combined %>%
  mutate(Rho.peel = factor(Rho.peel, levels = unique(Rho.peel)))

ggplot(tablebias_combined, aes(x = Rho.peel, y = Rho.Rho, group = Model, fill = Model)) +
  geom_point(size = 3, shape = 21, color = "black") +  
  geom_hline(yintercept = 0, color = "grey") +
  facet_wrap(~Quant, scales = "free_y") + 
  scale_fill_manual(name = "Scenario",
                    values = c("s1.1" = "#ca0020", 
                               "s1.2" = "#f4a582", 
                               "s1.3" = "#bababa", 
                               "s1.4" = "#404040")) +
  scale_color_manual(name = "Scenario",
                     values = c("s1.1" = "#ca0020", 
                                "s1.2" = "#f4a582", 
                                "s1.3" = "#bababa", 
                                "s1.4" = "#404040")) +
  theme_minimal() +
  labs(title = "",
       x = "",
       y = "Rho Value") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom")

The plot presents the retrospective bias (*Rho*) in Spawning Stock Biomass (SSB) and Fishing Mortality (F) across different peel years (2019–2016) and for the combined period under four model scenarios (s1.1 to s1.4). In the SSB panel, all models exhibit negative *Rho* values across the years, indicating a downward bias. The magnitude of the bias varies among models, with s1.3 and s1.4 showing the most pronounced deviations. In the F panel, *Rho* values are consistently positive, suggesting an upward bias. The combined *Rho* values for each metric confirm these trends, showing persistent differences among model scenarios.

(Discussion)

The observed retrospective bias in SSB and F aligns with findings from previous studies on krill population dynamics, where recruitment variability and model structure influence stock assessment estimates (Hill et al., 2016; Watters et al., 2020). The negative bias in SSB suggests that models may overestimate past biomass, potentially due to unaccounted environmental variability or underestimation of natural mortality (Meyer et al., 2021). The positive bias in F indicates a tendency to underestimate past fishing mortality, which could be linked to the inclusion of predator-based indices such as penguin foraging data (Trathan et al., 2018). These results highlight the importance of incorporating ecosystem interactions into stock assessments to improve predictive accuracy and support sustainable management of Antarctic krill.

@@

```{r eval=FALSE}
#### R0_profile_plot_Survey_like ----
png(file.path(plotdir,"R0_profile_plot_Survey_like.png"),
    width=7,
    height=4.5,
    res=300,
    units='in')
par(mar=c(5,4,1,1))
PinerPlot(prof.R0.summary, 
          profile.string = "R0", 
          component = "Surv_like",
          main = "Changes in Index likelihoods by fleet",
          add_cutoff = TRUE,
          cutoff_prob = 0.95, legendloc="topleft")
Baseval <- round(Base$parameters$Value[grep("SR_LN",
                                            Base$parameters$Label)],2)
Baselab <- paste(Baseval,sep="")
axis(1,at=Baseval,label=Baselab)
abline(v = Baseval, lty=2)
dev.off()
```

## Outputs

@@

```{r}
# Unir los data frames en uno solo
outpsall <- rbind(outps1,  
                  outps2,
                  outps3,
                outps4)
```

```{r}
# Crear una columna de modelo en cada data frame
outps1$Model <- "Ref Model: No Env-Predator"
outps2$Model <- "s1.2 w/ Predator data"
outps3$Model <- "s1.3 w/ Env data"
outps4$Model <- "s1.4 w/ Env and Predator data"

# Unir los data frames en uno solo
outpsall <- rbind(outps1,  outps4)

outpsall_long <- outpsall %>%
  pivot_longer(cols = c(Bio_smry, SpawnBio, Recruit_0), 
               names_to = "Variable", values_to = "Value")

# Gráfico de barras agrupadas por variable y modelo
ggplot(outpsall_long, aes(x = factor(Yr), y = Value, fill = Model)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Variable, 
             ncol=1,
             scales = "free_y") + 
  scale_fill_manual(name= "Scenario",
                    values = c("Ref Model: No Env-Predator" = "#ca0020",

                               "s1.4 w/ Env and Predator data" = "#404040")) +
  labs(title = "",
       x = "", y = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom")
```

@@

#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist <- SSgetoutput(keyvec = NULL,
                       dirvec = c(dir1.1,
                                  dir1.2,
                                  dir1.3,
                                  dir1.4),
                       getcovar = F)
summaryoutputall <- SSsummarize(biglist)
```

```{r}
legend.labels <- c('s1.1','s1.2','s1.3', 's1.4')

@@

#create summary of model runs from list above
summaryoutput <- SSsummarize(biglist)

tablelike <- SStableComparisons(summaryoutput,
                   likenames = c("TOTAL",
                                 "Survey",
                                 "Length_comp",
                                 "Age_comp",
                                 "priors",
                                 "Size_at_age"), 
                   names = c("Recr_Virgin",
                             "R0",
                             "SSB_Virg", 
                             "Bratio_2020",
                             "SPRratio_2020"),
                   digits = NULL,
                   modelnames = legend.labels,
                   csv=TRUE,
                   csvdir = "/Users/mauriciomardones/DOCAS/SA_Krill",
                   csvfile = "parameter_comparison_table.csv", verbose = TRUE,
                   mcmc = FALSE)
kbl(tablelike, booktabs = T,
    format = "html",
    caption = "")  %>% 
    kable_styling(latex_options = "scale_down")
```

@@

### Comparsion in sd long term time series forecasting

```{r fig.height=5, fig.width=8}

errt <- data.frame(
  Bio_all_1 = base.model1.1$timeseries$Bio_all,
  Bio_all_2 = base.model1.2$timeseries$Bio_all,
  Bio_all_3 = base.model1.3$timeseries$Bio_all,
  Bio_all_4 = base.model1.4$timeseries$Bio_all,

  Bio_smry_1 = base.model1.1$timeseries$Bio_smry,
  Bio_smry_2 = base.model1.2$timeseries$Bio_smry,
  Bio_smry_3 = base.model1.3$timeseries$Bio_smry,
  Bio_smry_4 = base.model1.4$timeseries$Bio_smry,

  SpawnBio_1 = base.model1.1$timeseries$SpawnBio,
  SpawnBio_2 = base.model1.2$timeseries$SpawnBio,
  SpawnBio_3 = base.model1.3$timeseries$SpawnBio,
  SpawnBio_4 = base.model1.4$timeseries$SpawnBio,

  Recruit_0_1 = base.model1.1$timeseries$Recruit_0,
  Recruit_0_2 = base.model1.2$timeseries$Recruit_0,
  Recruit_0_3 = base.model1.3$timeseries$Recruit_0,
  Recruit_0_4 = base.model1.4$timeseries$Recruit_0
)

err_long <- errt %>%
  pivot_longer(cols = everything(), 
               names_to = "Variable_Model",
               values_to = "Value")

err_long <- err_long %>%
  extract(Variable_Model, into = c("Variable", "Model"), 
          regex = "(.+?)_(\\d+)$")

err_long <- err_long %>%
  mutate(Model = case_when(
    Model == "1" ~ "Ref Model: No Env-Predator",
    Model == "2" ~ "S1.1 w/ Predator data",
    Model == "3" ~ "S1.1 w/ Env data",
    Model == "4" ~ "S1.1 w/ Env and Predator data",
    TRUE ~ Model
  ))

ggplot(err_long, aes(x = Model, y = Value, fill = Model)) +
  geom_boxplot(width = 0.5, outlier.shape = NA,
               outliers = F) +
  #geom_jitter(width = 0.2, alpha = 0.1) +
  facet_wrap(~Variable, ncol=4, 
             scales = "free_y") +
  scale_fill_manual(name = "Scenario",
                    values = c("#ca0020", "#f4a582", "#bababa", "#404040")) +
  labs(title = "",
       x = "",
       y = "") +
  theme_few() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")
```

Statistical diferences

```{r}
# Extraer los datos
spawn_bio_1 <- base.model1.1$timeseries$SpawnBio
spawn_bio_4 <- base.model1.4$timeseries$SpawnBio

# Prueba de normalidad (Shapiro-Wilk)
shapiro.test(spawn_bio_1)
shapiro.test(spawn_bio_4)

# Prueba de igualdad de varianzas (Levene)
library(car)
leveneTest(c(spawn_bio_1, spawn_bio_4), 
           group = rep(c("Model 1.1", "Model 1.4"), each = length(spawn_bio_1)))

# Prueba t de Student (si los datos son normales)
t.test(spawn_bio_1, spawn_bio_4, var.equal = TRUE)

# Prueba de Wilcoxon (si los datos no son normales)
wilcox.test(spawn_bio_1, spawn_bio_4)

**Two-Sample t-Test**

- **t-value:** 4.2682  
- **Degrees of Freedom (df):** 72  
- **p-value:** 5.915e-05 (very small)  
- **95% Confidence Interval for the Mean Difference:** [1,387,011; 3,818,074]  
- **Sample Means:**  
  - Model 1.1: **4,600,304**  
  - Model 1.4: **1,997,762**

Since the **p-value (5.915e-05) is much smaller than 0.05**, we reject the null hypothesis. This means there is **a statistically significant difference** between the spawning biomass predicted by Model 1.1 and Model 1.4. The confidence interval suggests that Model 1.1 tends to estimate a higher spawning biomass than Model 1.4, with an estimated difference between **1.39 and 3.82 million tons**.

**Wilcoxon Rank Sum Test (Mann-Whitney U Test)**

- **W-statistic:** 1256  
- **p-value:** 6.698e-10 (extremely small)  
- **Warning:** "Cannot compute exact p-value with ties" (indicates that some values are repeated)

The **Wilcoxon test also rejects the null hypothesis** with an extremely small **p-value (6.698e-10)**. This confirms that the distribution of spawning biomass values is significantly different between the two models. Since the Wilcoxon test does not assume normality, it supports the conclusion from the **t-test**, reinforcing that

Both tests strongly indicate that **Model 1.1 and Model 1.4 produce significantly different estimates of spawning biomass**. Specifically, **Model 1.1 predicts higher values**. This suggests that the factors or assumptions included in Model 1.4 result in **lower spawning biomass estimates**, which could have important implications for stock assessment and fisheries management.

@@

```{r}
df1 <- base.model1.1$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.1$likelihoods_used), Modelo = "s1.1")
df2 <- base.model1.2$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.2$likelihoods_used), Modelo = "s1.2")
df3 <- base.model1.3$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.3$likelihoods_used), Modelo = "s1.3")
df4 <- base.model1.4$likelihoods_used %>%
  select(values) %>%
  mutate(Componente = rownames(base.model1.4$likelihoods_used), Modelo = "s1.4")

df <- bind_rows(df1, 
                df2,
                df3,
                df4)
ggplot(df %>% 
         filter(values > 1), aes(x = Componente, y = values, fill = Modelo)) +
  geom_col(position = position_dodge(), width = 0.7) +  
  theme_few() +
  coord_flip() +  
  scale_fill_manual(name= "Scenario",
                    values = c("s1.1" = '#ca0020',
                               "s1.2" = '#f4a582', 
                               "s1.3" = '#bababa',
                               "s1.4" = '#404040')) + 
  labs(x = "",
       y = "Log-Normal Likelihood", 
       title = "") 
```
This bar plot presents the log-normal likelihood contributions of different model components in an Antarctic krill stock assessment under four scenarios (s1.1, s1.2, s1.3, and s1.4).

**TOTAL Likelihood:** The overall likelihood is highest for scenario s1.4 (black), followed by s1.2 (light orange). This suggests that s1.4 provides the best overall model fit, while s1.1 (dark red) has the lowest likelihood, indicating a poorer fit.  
**Survey Component:** The survey likelihood follows a similar pattern, with s1.4 and s1.2 showing better agreement with the data compared to s1.1.  
**Recruitment, Parameter Priors, and Parameter Deviations:** These components contribute minimally to the total likelihood, indicating that they do not heavily influence model fit differences.  
**Length Composition:** There is some variation in this component, with s1.2 showing a larger contribution than s1.1 and s1.3.

### **Overall Conclusion:**  
Scenario s1.4 seems to fit the data best, followed closely by s1.2. Scenario s1.1 has the poorest likelihood, meaning it is the least supported by the data. If s1.4 includes both environmental and predator effects, this suggests that incorporating ecosystem variables significantly improves the stock assessment model for Antarctic krill.
